Price of Anarchy for Mean Field Games

### 2018-08-03 PoA.tex
added remark connection Theorem 2 and prop 1

\begin{proposition}
Assuming (\ref{eq:assumptions}), if furthermore,
\begin{equation*}
\begin{split}
    \left[\bar{b}_1\bar{\eta}_t^{MKV}+s\bar{q}(s-1)\right]\bar{x}_t^{MKV}&=0,\ \forall t \in [0,T] \\
    (c^{MFG}-c^{MKV})(b_2+\bar{b}_2)\bar{\eta}_t^{MKV}\bar{x}_t^{MKV}&=0,\ \forall t \in [0,T] \\
    s_T\bar{q}_T(s_T-1)\bar{x}_T^{MKV}&=0,
\end{split}
\end{equation*}
then $PoA=1$.
\label{eq:lq_prop}
\end{proposition}

@@

\begin{corollary}
	Assuming (\ref{eq:assumptions}), if the initial condition $\xi$ is such that $\mathbb{E}(\xi)=0$, then from equation (\ref{eq:x_bar_MKV_explicit}), $x^{MKV}_t =0$ for all $t\in[0,T]$, and thus, $PoA=1$.
\end{corollary}

@@

>>>>

\begin{proposition}
Assuming (\ref{eq:assumptions}), if furthermore,
\begin{equation}
    \left[\bar{b}_1\bar{\eta}_t^{MKV}+s\bar{q}(s-1)\right]\bar{x}_t^{MKV}=0,\ \forall t \in [0,T] \label{eq:prop_1_1}
\end{equation}
\begin{equation}
    (c^{MFG}-c^{MKV})(b_2+\bar{b}_2)\bar{\eta}_t^{MKV}\bar{x}_t^{MKV}=0,\ \forall t \in [0,T]\label{eq:prop_1_2}
\end{equation}
\begin{equation}
    s_T\bar{q}_T(s_T-1)\bar{x}_T^{MKV}=0, \label{eq:prop_1_3}
\end{equation}
then $PoA=1$.
\label{eq:lq_prop}
\end{proposition}

@@

\begin{corollary}
	Assuming (\ref{eq:assumptions}), if the initial condition $\xi$ is such that $\mathbb{E}(\xi)=0$, then from equation (\ref{eq:x_bar_MKV_explicit}), $x^{MKV}_t =0$ for all $t\in[0,T]$, and thus, $PoA=1$.
	\label{corollary_2}
\end{corollary}

@@

\begin{remark}
	Assume (\ref{eq:assumptions}) and $\lambda=1$. Then Theorem \ref{thm:PoA_equivalent_1} tells us that the sufficient condition (equations (\ref{eq:prop_1_1})-(\ref{eq:prop_1_3})) from Proposition \ref{eq:lq_prop} is also a necessary condition to have $PoA=1$. To see this, assume $PoA=1$. Since $\lambda=1$, we have $c^{MFG}=c^{MKV}$ and thus, condition (\ref{eq:prop_1_2}) holds. If $\mathbb{E}(\xi)=0$, clearly conditions (\ref{eq:prop_1_1})-(\ref{eq:prop_1_3}) hold, as noted in Corollary \ref{corollary_2}. If $\mathbb{E}(\xi) \neq 1$ and $\bar{b}_1=0$, from Theorem \ref{thm:PoA_equivalent_1}, we have $D^u=D^w$ and $C^u=C^w$ which together with $\lambda=1$ imply conditions (\ref{eq:prop_1_1}) and (\ref{eq:prop_1_3}), similarly as Corollary \ref{corollary_1}. Now, if $\mathbb{E}(\xi) \neq 1$ and $\bar{b}_1>0$, from Theorem \ref{thm:PoA_equivalent_1}, we have $D^u=D^w$ which implies condition (\ref{eq:prop_1_3}). Finally, the condition $B(D)^2+2A^uD-C^u=B(D)^2+2A^wD-C^w=0$ implies $\bar{\eta}^{MKV}_t=w_t=D=\frac{C^u-C^w}{2(A^u-A^2)}=\frac{s\bar{q}(1-s)}{\bar{b}_1}$ and thus, we have condition (\ref{eq:prop_1_1}). In particular, recall that $\lambda=1$ for standard mean field games, where $\bar{b}_2=0$ and $\bar{r}=0$.
\end{remark}
